---
title: "Plot_TI_fields"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

.libPaths('C:/Users/vbeliaev/Documents/r_packages')

library(ggplot2)
library(data.table)
library(ggrepel)


```

## Plotting the TI fields 

This script, first, loads the database of the TI fields collected to find an optimal configuration of electrodes  
to stimulation of the vmPFC.     
Then, fields are sorted for focality of their stimulation.     
After that, we choose a field, which is not only focal, but also has one of the highest thresholds. 

Threshold correponds to the value of the median activation within the vmPFC (half of the voxels within the 
target are activated on the level of the threshold or higher).     
Focality tells us the percentage of the voxels activated higher than the threshold that are located within the target in comparison with the whole brain.      


```{r load TI fields, warning = FALSE}

setwd('C:/Users/vbeliaev/Documents/TI_fMRI/pre_registration_paper/methods/modelling/paper_scripts')
dat = read.csv('fields_729.csv')

dat_sort = dat[order(-dat$focality),]
dat_sort_red = dat_sort[1:10,]

dat_show = dat_sort_red[,c(1, 3, 6, 10, 11)]

knitr::kable(dat_show, caption = "Fields with highest focality")

```


Field which has high focality and high median field is 'Fp1 P7 Fp2 P8'   
This field will be highlighted on the plot   

Generating a plot for these results    

```{r generating the plot for the TI fields, echo = FALSE}

## highliting the field that is chosen  

idx = which(dat_sort_red$Field == 'Configuration_Fp1_P7_Fp2_P8.cache')
dat_sort_red$chosen = c(rep('unchosen', idx-1), rep('chosen', 1), rep('unchosen', nrow(dat_sort_red) - idx))

## preparing names of the fields for plots

vec_lab = as.character(dat_sort_red$Field)
new_names = c()
n = 1 
for (i_v in vec_lab) {
  
  i_spl = strsplit(i_v, '.cache')
  vec_spl = strsplit(i_spl[[1]], '_')
  
  new_names[n] = paste(vec_spl[[1]][2], vec_spl[[1]][3], 'and', vec_spl[[1]][4], vec_spl[[1]][5])
  n = n + 1
}

.labs = new_names

## plotting 

ggplot(dat_sort_red, aes(threshold, focality)) + 
  geom_point(aes(shape = chosen, color = chosen), size=4) + 
  xlab('Threshold (median TI field)') + 
  ylab('Focality (%)') + 
  theme_bw() + 
  #geom_text_repel(aes(label = .labs), size = 4) + 
  geom_label_repel(aes(label = .labs), size = 4) + 
  theme(text = element_text(size=14), axis.text.x = element_text(size=14), 
        axis.text.y = element_text(size=14)) + 
  ggtitle('Ten TI fields with best focality for vmPFC') + 
  theme(legend.position = "none") + 
  scale_shape_manual(values=c(17, 16)) + 
  scale_color_manual(values=c('darkviolet', 'gray21'))  

```

