---
title: "Pilot data analysis"
author: "valeriia beliaeva"
date: "11/8/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=TRUE, warning=FALSE, message=FALSE}
.libPaths('C:/Users/vbeliaev/Documents/r_packages')

knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library(ggsignif)
library(ggplot2)
library(gridExtra)
library(lme4)
library(plyr)
library(dplyr)
library(boot)
library(data.table)

'%!in%' <- function(x,y)!('%in%'(x,y))

```


# Data analysis Part I
# Behavioral calibration 

Data analysis is separated into 2 parts:     
1) we test whether the task is working correctly (Behavioral calibration)       
2) we test the effect of TI stimulation on choice consistency / accuracy     
(vmPFC TI neuromodulation)     

In this file the first part of the data analysis is presented.    

Main dependent variable is choice consistency / accuracy

Correct answers (variable corr) correspond to trials, in which participant has chosen a picture, which 
was earlier rated higher during the rating task. For example, participant during the rating task 
estimated taste of banana for 0.8 and Twix for 0.9. Then in the choice task, when twix and banana 
are presented in the same trial, if participant chooses Twix, answer is correct, if they choose banana
the answer is considered incorrect.  


```{r load data, warning=FALSE, message=FALSE}

# loading preprocessed data

setwd('C:/Users/vbeliaev/Documents/TI_fMRI/pre_registration_paper/methods/pilot_scripts_paper')
tab1 = as.data.table(read.csv("Data_collected_together_preprocessed.csv"))

dataVal = tab1[Cue_Taste1_Size2 == 1]
dataVal$Taste_diff.abs = scale(abs(dataVal$Taste_diff))
dataVal$Size_diff.abs = scale(abs(dataVal$Size_diff))

dataPer = tab1[Cue_Taste1_Size2 == 2]
dataPer$Taste_diff.abs = scale(abs(dataPer$Taste_diff))
dataPer$Size_diff.abs = scale(abs(dataPer$Size_diff))

ns = length(unique(tab1$Participant))


```


## RUN MODELS 

First, verifying impact of taste difference on accuracy in value-based trials.    

```{r value trials , warning=FALSE, message=FALSE}

m1.val = glmer(corr ~ Size_diff.abs + Taste_diff.abs + (1+Size_diff.abs + Taste_diff.abs|Participant), data=dataVal, family=binomial(link = "logit"))
s1 = summary(m1.val)

s1
```

Second, verifying impact of size difference on accuracy in perceptual trials.    

```{r size trials , warning=FALSE, message=FALSE}

m1.per = glmer(corr ~ Size_diff.abs + Taste_diff.abs + (1+Size_diff.abs + Taste_diff.abs|Participant), data=dataPer, family=binomial(link = "logit"))
s2 = summary(m1.per)

s2
```


## PLOTS 

Plot 1
Now, plot the resulting beta estimates of the models above.     

```{r plot betas , warning=FALSE, message=FALSE}


plot_betas = as.data.table(matrix(c(s1$coefficients[2,1], s1$coefficients[3,1], 
                      s2$coefficients[2,1], s2$coefficients[3,1], 
                      s1$coefficients[2,2], s1$coefficients[3,2], 
                      s2$coefficients[2,2], s2$coefficients[3,2]), nrow = 4, ncol = 2))

colnames(plot_betas) = c('beta_mean', 'beta_std')
plot_betas$cue = rep(c("Perceptual trials", "Value-based trials"), each = 2)
plot_betas$cue = factor(plot_betas$cue, levels = c('Value-based trials', 'Perceptual trials'))

plot_betas$ratings = rep(c("Size", "Taste"), 2)
plot_betas$ratings = factor(plot_betas$ratings, levels = c('Taste', 'Size'))

p_betas = ggplot(plot_betas, aes(x=cue, y=beta_mean, fill = ratings)) +
  geom_bar(stat="identity", position=position_dodge(), alpha = 0.5, color = 'black') +
  geom_errorbar(aes(ymin=beta_mean-beta_std, ymax=beta_mean+beta_std), width=.1,
                position=position_dodge(.9)) + 
  geom_point(position=position_dodge(.9), show_guide = FALSE) + 
  theme_bw() + 
  ylab('Beta estimates') + 
  xlab(' ') +
  scale_fill_manual(values=c('darkred', 'grey48')) + 
  ggtitle('Impact of a cue on choice consistency') + 
  coord_cartesian(ylim= c(-0.1,1)) + 
  theme(text = element_text(size=16), axis.text.x = element_text(size=16, colour = 'black'), 
        axis.text.y = element_text(size=16), legend.text=element_text(size=16)) +
  theme(legend.position = c(0.2, 0.87))  +
  guides(fill=guide_legend(title="Difference in ratings")) + 
  theme(legend.background=element_blank()) + 
  annotate('text', x = 0.78, y = 0.10, label = 'NS') + 
  annotate('text', x = 1.22, y = 0.85, label = '***') + 
  annotate('text', x = 1.77, y = 0.76, label = '***') + 
  annotate('text', x = 2.22, y = 0.10, label = 'NS')  

p_betas

plot_dir = 'C:/Users/vbeliaev/Documents/TI_fMRI/pre_registration_paper/methods/paper_scripts_v4'
#ggsave('p_betas.png',  path = plot_dir, dpi=300)

```


Plot 2 / probability of choosing top image     

Here we plot the dependecy between difference in ratings between the top and the bottom picture and the choice.   
In this plot dependent varible is choice top picture (1) or bottom (0).    

Differences in ratings of taste or size are grouped in tiles from 1 to 4. Negative tiles represent conditions, when food items presented in the bottom of the screen during the choice task were higher estimated than items shown at the top. The larger is the number of the tile the lager is the difference in ratings between two food items.     


```{r s plot , warning=FALSE, message=FALSE}

# Taste trials 
tmp_val = ddply(dataVal, .(Participant,Taste_diff.ntile), summarise, acc = mean(Choice01))
tmp_val = ddply(tmp_val, .(Taste_diff.ntile), summarise, acc2 = mean(acc), se=sd(acc)/sqrt(ns))
tmp_val$cue = "Taste"
colnames(tmp_val)[1] = "diff"

tmp_per = ddply(dataVal, .(Participant,Size_diff.ntile), summarise, acc = mean(Choice01))
tmp_per = ddply(tmp_per, .(Size_diff.ntile), summarise, acc2 = mean(acc), se=sd(acc)/sqrt(ns))
tmp_per$cue = "Size"
colnames(tmp_per)[1] = "diff"

tmp_val_per = rbind(tmp_val,tmp_per)

colors =c('darkred', 'grey48')
limits = aes(ymax = acc2+se, ymin=acc2-se, colour=cue, group=cue)
tmp_val_per$diff = factor(tmp_val_per$diff, labels = c(-4,-3,-2,-1, 1, 2, 3, 4))
tmp_val_per$cue = factor(tmp_val_per$cue, levels = c('Taste', 'Size'))

p1.val = ggplot(tmp_val_per, aes(diff, acc2, group=cue)) +
  geom_line(aes(colour=cue), size=2, alpha = 0.5) +
  geom_errorbar(limits, width=0.25, size=1) +
  geom_point(aes(shape=cue, colour=cue), size=4) +
  scale_colour_manual(values=colors) +
  theme_bw() + 
  ylab("Probability choose top item") + xlab("Difference in ratings (top item - bottom)") + 
  theme(axis.title=element_text(size=10)) + theme(axis.text=element_text(size=10)) +
  theme(legend.text=element_text(size=17)) +
  coord_cartesian(ylim = c(0, 1)) +
  ggtitle("Value-based trials") + 
  theme(legend.title = element_blank()) + 
  theme(text = element_text(size=16), axis.text.x = element_text(size=16), 
        axis.text.y = element_text(size=16)) +
  theme(legend.position = c(0.2, 0.87)) + 
  theme(legend.background=element_blank()) 

#p1.val

# Size trials 

tmp_val = ddply(dataPer, .(Participant,Taste_diff.ntile), summarise, acc = mean(Choice01))
tmp_val = ddply(tmp_val, .(Taste_diff.ntile), summarise, acc2 = mean(acc), se=sd(acc)/sqrt(ns))
tmp_val$cue = "Taste"
colnames(tmp_val)[1] = "diff"

tmp_per = ddply(dataPer, .(Participant,Size_diff.ntile), summarise, acc = mean(Choice01))
tmp_per = ddply(tmp_per, .(Size_diff.ntile), summarise, acc2 = mean(acc), se=sd(acc)/sqrt(ns))
tmp_per$cue = "Size"
colnames(tmp_per)[1] = "diff"

tmp_val_per = rbind(tmp_val,tmp_per)

colors =c('darkred', 'grey48')
limits = aes(ymax = acc2+se, ymin=acc2-se, colour=cue, group=cue)
tmp_val_per$diff = factor(tmp_val_per$diff, labels = c(-4,-3,-2,-1, 1, 2, 3, 4))
tmp_val_per$cue = factor(tmp_val_per$cue, levels = c('Taste', 'Size'))

p1.per = ggplot(tmp_val_per, aes(diff, acc2, group=cue)) +
  geom_line(aes(colour=cue), size=2, alpha = 0.5) +
  geom_errorbar(limits, width=0.25, size=1) +
  geom_point(aes(shape=cue, colour=cue), size=4) +
  scale_colour_manual(values=colors) +
  theme_bw() + 
  ylab(" ") + 
  xlab(" ") + 
  theme(axis.title=element_text(size=17)) + theme(axis.text=element_text(size=17)) +
  theme(legend.text=element_text(size=17)) +
  coord_cartesian(ylim = c(0, 1)) +
  ggtitle("Perceptual trials") + 
  theme(legend.title = element_blank()) + 
  theme(text = element_text(size=16), axis.text.x = element_text(size=16), 
        axis.text.y = element_text(size=16)) +
  theme(legend.position = "none") + 
  theme(legend.background=element_blank()) 

grid.arrange(p1.val, p1.per, ncol=2, widths=c(1,1))
#g = arrangeGrob(p1.val, p1.per, ncol=2)
#ggsave('p_prob_choose.png',  g, path = plot_dir, dpi=300)

```

